---
title: "data_preprocessing_empatica_wesad.Rmd"
author: "Jingjing Shi, Jack Li, Vinayak Pathak"
date: "11/13/2020"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Loading the appropriate libraries for the project
```{r}
library(psych)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(pracma)
library(SynchWave)
library(corrplot)
library(rmatio)
library(reticulate)
library(matlab)
library(lubridate)
library("gtools")
library(zoo)
```

```{r}
plist<-as.integer(c(2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 13, 14, 15, 16, 17))
```

```{r}
file_main="C:\\Users\\COLDD03\\Desktop\\Project_Dataset\\WESAD\\S2\\S2_E4_Data\\"
```

```{r}
ACC<-read.csv2(paste0(file_main, "ACC.csv"),sep=",", header=FALSE)
lenacc<-nrow(ACC)
ACC<-ACC[3:lenacc,]
facc = 32
names(ACC)<-c("x", "y", "z")
l<-unlist(seq(1, lenacc-2))
ACC[["sno"]]<-l
```
```{r}
ACC<-ACC%>%
  mutate(time = (sno/(60*facc)))#Time in Seconds
```
```{r}
S2_quest<-read.csv2(file = "C:\\Users\\COLDD03\\Desktop\\Project_Dataset\\WESAD\\S2\\S2_quest.csv")
```
Conditions for Participants
1 = Baseline
2 = TSST/Stress
3 = Amusement
4 = Meditation
5  = b Read
6  = Slow Read
7  = fast Read

We will first create an interface for reading in the pickle data
```{r}
require("reticulate")
source_python("pickle_reader.py")
```
Now creating a list of filenames in the variable filen
```{r}
plist<-as.integer(c(2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 13, 14, 15, 16, 17))
```

```{r}
root_fold=c("C:\\Users\\COLDD03\\Desktop\\Project_Dataset\\WESAD")
filen=list()
a=1
for (i in plist)
  {
  base = paste("S",i, sep="")
  file = paste("S",i,".pkl",sep="")
  file_name<-paste(root_fold, base, file, sep="\\")
  filen<-append(filen[!is.na(filen)], file_name)
  a=a+1
}
```
All the file-names to be read are stored in the 'filen' variable, now we will sequentially read the corresponding pickle files..And store them in a prescribed format, After that we will apply time windowing and extract the features.
```{r}
filen[[1]]
```
Creating a new dataframe called data.raw WESAD
```{r}
facc = 32
fbvp = 64
feda = 4
ftemp  = 4
```
```{r}
data.raw.wesad=list()
for(i in c(1:1))#length(filen) replace the end 1 with length(filen)
{ pickle_data <- read_pickle_file(filen[[i]])
}

```

```{r}
x<-pickle_data$label
label_mean<-as.data.frame(rollapply(x, width = 700, FUN = min, by =700))
```
```{r}
unique(label_mean)
```
```{r}
count()
```
```{r}
x<-data.frame(x)

```
Following code stores the time series data of individual variables in form of list
```{r}
data.raw.wesad = list()
```

```{r}
for(i in c(1:length(filen)))
{ 
  pickle_data <- read_pickle_file(filen[[i]])
  len_data<-nrow(pickle_data$signal$wrist$TEMP)/4
  timesec =c(1:len_data)
  timemin = timesec/60.0
  Pat_ID  = plist[i]*(ones(nrow(len_data), 1))
  Index = c(1:len_data)
  acc_mean<-rollapply(pickle_data$signal$wrist$ACC, width = facc, FUN = mean, by =facc)
  eda_mean<-rollapply(pickle_data$signal$wrist$EDA, width = feda, FUN = mean, by =feda)
  bvp_mean<-rollapply(pickle_data$signal$wrist$BVP, width = fbvp, FUN = mean, by =fbvp)
  temp_mean<-rollapply(pickle_data$signal$wrist$TEMP, width = ftemp, FUN = mean, by =ftemp)
  #label<--rollapply(pickle_data$label, width = 700, FUN = max, by =700)
  data.raw.wesad[[i]]<-data.frame(Index = Index, EDA = eda_mean, ACC = acc_mean, BVP = bvp_mean, TEMP = temp_mean, lab = label, Pat_ID = Pat_ID, timesec = timesec, timemin = timemin)
}

```
```{r}
timeshifts = c(118.2514285714,33.81143,45.9057,42.8271,27.5029,27.7671,55.0671, 13.55286, 57.14143, 48.17429, 48.89286, 93.60286, 144.7686, 81.62857, 88.96429)
```
```{r}
for(i in c(1:length(filen)))
{
  data.raw.wesad[[i]]$timesec<-data.raw.wesad[[i]]$timesec+timeshifts[i]
  data.raw.wesad[[i]]$timemin<-(data.raw.wesad[[i]]$timesec)/(60.0)
}
```



```{r}

Sname<-list()

```
```{r}
for(i in c(1:length(plist)))
{
Sname<-append(Sname, paste0("S", plist[i], "_E4_final"))
}
```
```{r}
for(i in c(1:15))
{
   write_delim(data.raw.wesad[[i]], paste("C:\\Users\\COLDD03\\Desktop\\Project_Dataset\\WESAD\\wesad_e4_process\\WESAD_E4_Patient_data\\", Sname[[i]], ".csv", sep=""), delim = ",")
}

```
```{r}
Spat_combined<-do.call(rbind, data.raw.wesad)
```
```{r}
   write_delim(Spat_combined, paste("C:\\Users\\COLDD03\\Desktop\\Project_Dataset\\WESAD\\wesad_e4_process\\WESAD_E4_Patient_data\\", "Spat_combined", ".csv", sep=""), delim = ",")

```