---
title: "data_preprocessing_chest_wesad.Rmd"
author: "Jingjing Shi, Jack Li, Vinayak Pathak"
date: "11/13/2020"
output:
  html_document: default
  pdf_document: default
---
Loading the appropriate libraries for the project
```{r}
library(psych)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(pracma)
library(SynchWave)
library(corrplot)
library(rmatio)
library(reticulate)
library(matlab)
library(lubridate)
library("gtools")
```

We will first create an interface for reading in the pickle data
```{r}
require("reticulate")
source_python("pickle_reader.py")
```
Now creating a list of filenames in the variable filen
```{r}
plist<-as.integer(c(2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 13, 14, 15, 16, 17))
```
```{r}
plist[1]

```

##Reading the file names
```{r}
root_fold=c("C:\\Users\\COLDD03\\Desktop\\Project_Dataset\\WESAD")
filen=NA
a=1
for (i in plist)
  {
  base = paste("S",i, sep="")
  file = paste("S",i,".pkl",sep="")
  file_name<-paste(root_fold, base, file, sep="\\")
  filen<-append(filen[!is.na(filen)], file_name)
  a=a+1
}
```
All the file-names to be read are stored in the file, now we will sequentially read the corresponding pickle files..And store them in a prescribed format, After that we will apply time windowing and extract the features.
```{r}
fs = 700# 700 Hz
ts = 1/fs#Sampling timeline
data.raw=list()
```
```{r}
for(i in c(1:length(filen)))#length(filen) replace the end 1 with length(filen)
 { pickle_data <- read_pickle_file(filen[i])
  timesec =c(1:nrow(pickle_data["signal"]$signal$chest$EDA))/fs
  timemin = timesec/60.0
 
  data.raw[[i]]<-data.frame(Index =c(1:nrow(pickle_data["signal"]$signal$chest$EDA)),
                            Pat_ID  = plist[i]*(ones(nrow(pickle_data["signal"]$signal$chest$EDA), 1)), EDA=pickle_data["signal"]$signal$chest$EDA, ACC=pickle_data["signal"]$signal$chest$ACC,ECG=pickle_data["signal"]$signal$chest$ECG, EMG=pickle_data["signal"]$signal$chest$EMG,Temp=pickle_data["signal"]$signal$chest$Temp,
                            Resp=pickle_data["signal"]$signal$chest$Resp, 
                            lab=pickle_data["label"]$label, timesec = timesec, timemin = timemin)}
```
Adding the time vector
For each data frame add the uncorrected time vector.
```{r}
length(filen)
```
```{r}

```
```{r}
for(i in c(1:length(filen)))
{data.raw[[i]]%>%
    mutate(timesec = Index/700)
}

```
Extracting the Respiban signal from the data.frame

```{r}
#assign(paste("data.raw.S2$","S",5,sep=""),data.frame(signal=pickle_data["signal"]$signal$chest$EDA, lab = pickle_data["label"]$label))


```
Now creating a dataframe list with per second data sampled at 350 Hz
```{r}
fs = 700.000
fsorig =700.000
```
```{r}
len1 = (length(data.raw[[1]]$signal)/fs)
listparam=list(NULL, NULL, NULL, NULL, NULL, NULL, NULL, NULL)
#meanlist = list()
#minlist = list()
#maxlist = list()
#medianlist= list()
#skewlist = list()
#kurtosis = list()
#time=list()


```
```{r}
delta = fs/fsorig;
for(i in as.integer(c(1:len1))){
  listparam[[1]]<-rbind(listparam[[1]], (fs/fsorig)*(i-1))
  listparam[[2]]<-rbind(listparam[[2]], mean(data.raw[[1]]$signal[((i-1)*fs+1):(i*fs)]))
  listparam[[3]]<-rbind(listparam[[3]], min(data.raw[[1]]$signal[((i-1)*fs+1):(i*fs)]))
  listparam[[4]]<-rbind(listparam[[4]], max(data.raw[[1]]$signal[((i-1)*fs+1):(i*fs)]))
  listparam[[5]]<-rbind(listparam[[5]], median(data.raw[[1]]$signal[((i-1)*fs+1):(i*fs)]))
  listparam[[6]]<-rbind(listparam[[6]], skew(data.raw[[1]]$signal[((i-1)*fs+1):(i*fs)]))
  listparam[[7]]<-rbind(listparam[[7]], kurtosi(data.raw[[1]]$signal[((i-1)*fs+1):(i*fs)]))
  listparam[[8]]<-rbind(listparam[[8]], min(data.raw[[1]]$lab[((i-1)*fs+1):(i*fs)]))
  
}
```

```{r}
listparam<-data.frame(listparam)
```
```{r}
names(listparam)<-c("TIME", "MEAN", "MIN", "MAX", "MEDIAN", "SKEWNESS", "KURTOSIS", "CONDITION")

```
Verify if the conditions are correct or false
```{r}
unique(listparam$CONDITION)
  
```

#Now dividinng the last column into factor depending on if the the patient is stresed or not...

classifying the seven categories and then adding an additional category which classified if the person is under stress or not.

```{r}
listparam<-listparam %>%
  mutate(TIMEMIN = TIME/60.000)
```

Start Signal 2 from here
```{r}
S2_signal=list()
S2_signal$signal<-data.raw$S2$signal
S2_signal<-data.frame(S2_signal)
S2_signal[["lab"]]<-data.raw$S2$lab
  
```
Adding the count factor
```{r}
S2_signal[["counttime"]]<-c(1:length(data.raw$S2$lab))

```
Adding a time second data
```{r}
S2_signal<-S2_signal%>%
  mutate(timesec = as.numeric(counttime/fsorig))
```
Adding a time min data
```{r}
S2_signal<-S2_signal%>%
  mutate(timemin = timesec/60.000)
```
Adding a time sec corrected data
```{r}
S2_signal<-S2_signal%>%
  mutate(timeseccor = timesec+(424.8-306.54857142857144935988))
```
Adding a time min corrected data
```{r}
S2_signal<-S2_signal%>%
  mutate(timemincor = timeseccor/60.00)

```


Adding the time in mins
```{r}
S2_signal<-S2_signal%>%
  mutate(timemin=counttime/(700*60)+1.97)
```

1.97 = shift factor...
0=Nothing
1 = Baseline
2 = Stress/TSST
3 = Amusement
4 = Meditation
5 = 
6 = Slow Read
7 = Fast Read


Will Create 15 sets of patients dataframe as a processed dataset. 
Processing the first signal

plist<-as.integer(c(2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 13, 14, 15, 16, 17))
```{r}
S2<-data.raw[[1]]
```
The time factor additions
```{r}
S2$timesec<-S2$timesec+(424.8-306.54857142857144935988)
S2$timemin<-S2$timesec/60
```

```{r}
S3<-data.raw[[2]]
```
```{r}
S3$timesec<-S3$timesec+(386.4-352.58857)
S3$timemin<-S3$timesec/60
```
Conditions for S3
1 = Baseline
2 = TSST/Stress
3 = Amusement
4 = Meditation
5  = b Read
6  = Slow Read
7  = fast Read
```{r}
S4<-data.raw[[3]]

```
Applying time correction
```{r}
S4$timesec<-S4$timesec+(45.9057)
S4$timemin<-S4$timesec/60
```

```{r}
S5<-data.raw[[4]]
```
```{r}
S5$timesec<-S5$timesec+(42.8271)
S5$timemin<-S5$timesec/60
```

```{r}
S6<-data.raw[[5]]
```
```{r}
S6$timesec<-S6$timesec+(27.5029)
S6$timemin<-S6$timesec/60
```

```{r}
S7<-data.raw[[6]]
```
```{r}
S7$timesec<-S7$timesec+(27.7671)
S7$timemin<-S7$timesec/60
```
```{r}
S8<-data.raw[[7]]
```
```{r}
S8$timesec<-S8$timesec+(55.0671)
S8$timemin<-S8$timesec/60
```

```{r}
S9<-data.raw[[8]]

```
```{r}
S9$timesec<-S9$timesec+(13.55286)
S9$timemin<-S9$timesec/60
```
```{r}
S10<-data.raw[[9]]

```
```{r}
S10$timesec<-S10$timesec+(57.14143)
S10$timemin<-S10$timesec/60
```

```{r}
S11<-data.raw[[10]]
```

```{r}
S11$timesec<-S11$timesec+(48.17429)
S11$timemin<-S11$timesec/60
```

```{r}
S13<-data.raw[[11]]
```
```{r}
S13$timesec<-S13$timesec+(48.89286)
S13$timemin<-S13$timesec/60
```
```{r}
S14<-data.raw[[12]]
```

Conditions for S14
1 = Baseline
2 = TSST/Stress
3 = Amusement
4 = Meditation
5  = b Read
6  = Slow Read
7  = fast Read
```{r}
S14$timesec<-S14$timesec+(93.60286)
S14$timemin<-S14$timesec/60
```
```{r}
head(data.frame(S14[, 10:13])%>%filter(lab==2))
```
```{r}
tail(data.frame(S14[, 10:13])%>%filter(lab==2))
```
```{r}
S15<-data.raw[[13]]
```
```{r}
S15$timesec<-S15$timesec+(144.7686)
S15$timemin<-S15$timesec/60
```
```{r}
head(data.frame(S15[, 10:13])%>%filter(lab==4))
```
```{r}
tail(data.frame(S15[, 10:13])%>%filter(lab==4))
```


```{r}
S16<-data.raw[[14]]
```
```{r}
head(data.frame(S16[, 10:13])%>%filter(lab==4))
```
```{r}
tail(data.frame(S16[, 10:13])%>%filter(lab==4))
```


```{r}
S16$timesec<-S16$timesec+(81.62857)
S16$timemin<-S16$timesec/60
```

```{r}
S17<-data.raw[[15]]
```
```{r}
head(data.frame(S17[, 10:13])%>%filter(lab==2))
```
```{r}
tail(data.frame(S17[, 10:13])%>%filter(lab==2))
```
```{r}
S17$timesec<-S17$timesec+(88.96429)
S17$timemin<-S17$timesec/60
```
##Computing  1 sec time window rolling average using rollapply for each category and each patient
## Stride  = 700 datapoints, Rolling Window  = 700 datapoints.
Now I have to make a list of all the data frames and then call on all the data frames with while averaging out for each category...

```{r}
data.corrected = list(S2, S3, S4, S5, S6, S7, S8, S9, S10, S11, S3, S14, S15, S16, S17)

```
So basically there are four categories as below and we have to do a time average for values across these four categories: While rejecting other variables., Conditions for Any variables
1 = Baseline
2 = TSST/Stress
3 = Amusement
4 = Meditation


```{r EVAL = False}
rm(data.raw)
rm(pickle_data)

```
```{r}
rm(data.corrected)
```
1 = Baseline
2 = TSST/Stress
3 = Amusement
4 = Meditation

## The following code attempts to filter out each catgory and apply the rolling average, if it fails(subject to the computational load) then there is a backup code available after this


##This is the mega loop and requires lot of computational power to run and a lot of R memory to store the data so in whole  the original loop would look like c(1:15), to avoid that I have written the code as for (k in c(1:1), c(2:2), c(3:3).. and so on) i.e. running for each patient manually...

Now evaluating S17
```{r}
for(k in c(15:15))
{
  rm(gtemp1)
  rm(gtemp2)
  rm(gtemp3)
  rm(gtemp4)
  gtemp1 = list()
  gtemp2= list()
  gtemp3 = list()
  gtemp4 = list()
  rm(x)




for(i in c(3:13))
{
  x<-eval(as.name(name3[[k]]))%>%filter(lab==1)%>%
  select(i)
  
  gtemp1[[i-2]]<-as.data.frame(rollapply(x, width = 700, FUN = mean, by =700))
}


gtemp1<-data.frame(do.call(cbind, gtemp1))
rm(x)

for(i in c(3:13))
{
  x<-eval(as.name(name3[[k]]))%>%filter(lab==2)%>%
  select(i)
  
  gtemp2[[i-2]]<-as.data.frame(rollapply(x, width = 700, FUN = mean, by =700))
}


gtemp2<-data.frame(do.call(cbind, gtemp2))


rm(x)

for(i in c(3:13))
{
  x<-eval(as.name(name3[[k]]))%>%filter(lab==3)%>%
  select(i)
  
  gtemp3[[i-2]]<-as.data.frame(rollapply(x, width = 700, FUN = mean, by =700))
}

gtemp3<-data.frame(do.call(cbind, gtemp3))

rm(x)

for(i in c(3:13))
{
  x<-eval(as.name(name3[[k]]))%>%filter(lab==4)%>%
  select(i)
  
  gtemp4[[i-2]]<-as.data.frame(rollapply(x, width = 700, FUN = mean, by =700))
}



gtemp4<-data.frame(do.call(cbind, gtemp4))






assign(paste0(name3[[k]],"_final"), rbind(gtemp1, gtemp2, gtemp3, gtemp4))

}



```
```{r}
#(c(2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 13, 14, 15, 16, 17))
```

##Replace S17 with current patient name
```{r}
S17_final[["ID"]]<-(plist[k])*ones(nrow(S17_final), 1)
```

```{r}
#Writing the csv file
for(ki in name3)
{
write_excel_csv2(eval(as.name(paste0(ki, "_final"))), 
            
           file =paste0("C:\\Users\\COLDD03\\Desktop\\Project_Dataset\\WESAD_vp\\Patientwise_pre_processed_csv\\", ki,".csv"))

}
```

```{r}
S_combined<-rbind(S2_final,S3_final, S4_final, S5_final, S6_final, S7_final, S8_final, S9_final, S10_final, S11_final, S13_final, S14_final, S15_final, S16_final, S17_final)
```
```{r}
S_list<-list(S2_final,S3_final, S4_final, S5_final, S6_final, S7_final, S8_final, S9_final, S10_final, S11_final, S13_final, S14_final, S15_final, S16_final, S17_final)
```
```{r}
S_name<-c("S2_final","S3_final", "S4_final", "S5_final", "S6_final", "S7_final", "S8_final", "S9_final", "S10_final", "S11_final", "S13_final", "S14_final", "S15_final", "S16_final", "S17_final")
```

```{r}
 write_delim(S_combined, "C:\\Users\\COLDD03\\Desktop\\Project_Dataset\\WESAD_vp\\WESAD_combined_dataset.csv", delim = ",")
```
```{r}
Stest<-read.csv2("C:\\Users\\COLDD03\\Desktop\\Project_Dataset\\WESAD_vp\\WESAD_combined_dataset.csv", sep = ",")

```
```{r}
for(i in c(1:15))
{
   write_delim(S_list[[i]], paste("C:\\Users\\COLDD03\\Desktop\\Project_Dataset\\WESAD_vp\\Patientwise_pre_processed_csv\\", S_name[[i]], ".csv", sep=""), delim = ",")
}



```